Systematic studies of correlations between different order flow harmonics in Pb--Pb collisions at $\mathbf{\sqrt{s_{\rm NN}}}$ = 2.76 TeV

### 2017-11-13 longSC.tex
eps to pdf

\begin{figure*}[t!]
            \begin{center}
                       \resizebox{0.51\textwidth}{!}{\includegraphics{figs/Fig1a_higherSC.eps}}\hspace{-0.67cm}
                       \resizebox{0.51\textwidth}{!}{\includegraphics{figs/Fig1b_higherNSC.eps}}
        \caption{The centrality dependence of SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonics for m = 3--5 and n = 2,3 in $\PbPb$ collisions at $\snn=2.76$~TeV. The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from \cite{ALICE:2016kpq} and shown as bands. The systematic and statistical errors are combined in quadrature for these lower order harmonic correlations. The SC(4,2) and SC(3,2) are downscaled by a factor of 0.1. Systematic uncertainties are represented with boxes for higher order harmonic correlations.}
        \label{fig:Figure_1}
              \end{center}
\end{figure*}

@@

\begin{figure}[t!]
	\begin{center}
        	\resizebox{0.92\columnwidth}{!}{\includegraphics{figs/Fig2_pt_SC_NSC.eps}}
        \caption{SC(3,2) and SC(4,2) ((a) and (c)) as a function of minimum $p_{\rm T}$ cuts in $\PbPb$ collisions at $\snn=2.76$~TeV are shown in the left panels. The NSC(3,2) and NSC(4,2) ((b) and (d)) are shown in the right panels. Systematic uncertainties are represented with boxes.}         \label{fig:Figure_2}
        \end{center}   
\end{figure}

@@

\begin{figure}[t!]
	\begin{center}
        	\resizebox{0.92\columnwidth}{!}{\includegraphics{figs/Fig3_vn_xpt.eps}}
        \caption{The individual flow harmonics $v_n$ for $n$ = 2--5 in $\PbPb$ collisions at $\snn=2.76$~TeV are shown in the left panels ((A), (B) and (C)). $v_4$ and $v_5$ are shown in the same panel (C). The $p_{\rm T, min}$ dependence of $v_n$ for $n$ = 2--4 is shown in the right panels ((a), (b) and (c)).}
        \label{fig:Figure_3}
        \end{center}   
\end{figure}

@@

\begin{figure}[t!]
            \begin{center}
                       \resizebox{\multfigsize\textwidth}{!}{\includegraphics{figs/Fig4_ModelComparison_EKRT.eps}}
              \end{center}
        \caption{The centrality dependence of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV. Results are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}. The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations. Left (right) panels show SC($m$,$n$) (NSC($m$,$n$)).}        
        \label{fig:Figure_4}
\end{figure}

@@

\begin{figure}[t!]
	\begin{center}
        	\resizebox{\multfigsize\columnwidth}{!}{\includegraphics{figs/Fig5_ModelComparison_VISH.eps}}
        \caption{The centrality dependence of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV. Results are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}. Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers. The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber and 0.16 for AMPT) are drawn as dashed lines. Left (right) panels show SC($m$,$n$)  (NSC($m$,$n$)).}
        \label{fig:Figure_5}
        \end{center}   
 \end{figure}

@@

 \begin{figure}[t!]
	\begin{center}
        	\resizebox{\multfigsize\columnwidth}{!}{\includegraphics{figs/Fig6_ModelComparison_AMPT.eps}}
        \caption{The centrality dependence of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV. Results are compared to various AMPT models. Left (right) panels show SC($m$,$n$)  (NSC($m$,$n$).}
        \label{fig:Figure_6}
        \end{center}   
 \end{figure}

@@

\begin{figure}[t!]
            \begin{center}
                       \resizebox{0.99\textwidth}{!}{\includegraphics{figs/Fig7_chisqndf_bestfits_3pad.eps}}
        \caption{The $\chisqndf$ values calculated by Eq.~\ref{Eq:chisq} are shown for SC($m$,$n$) (a), NSC($m$,$n$) (b) and individual harmonics $v_n$ (c). Results are for model calculations which are best in describing the SC observables for each of the three different types of models.}
        \label{fig:Figure_7}
              \end{center}
\end{figure}
The results for SC($m$,$n$) and NSC($m$,$n$) are presented in Fig.~\ref{fig:Figure_7}a and \ref{fig:Figure_7}b, respectively. The $\chisqndf$ values for the individual flow harmonics $v_n$ for $n$=2--4 are shown in Fig.~\ref{fig:Figure_7}c. We found that in case of the calculations from VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08) and the default configuration of the AMPT model, the $\chisqndf$ values for SC($m$,$n$) are larger than those for NSC($m$,$n$). This reflects the fact that the individual flow harmonics $v_n$ are not well described by those models compared to event-by-event EKRT+viscous hydrodynamics. This is quantified in Fig.~\ref{fig:Figure_7}c, where the $\chisqndf$ values for $v_n$ are much larger both for VISH2+1 and default AMPT calculations than event-by-event EKRT+viscous hydrodynamics.
The default configuration of the AMPT model gives the best $\chisqndf$ values for NSC($m$,$n$), especially for NSC(3,2). However the $\chisqndf$ values of this model are largest for $v_n$ among the models especially for $v_2$.

@@

\subsection{Transverse Momentum Dependence of Correlations between $v_2$ and $v_3$ and between $v_2$ and $v_4$}
\label{sec:ptdepsc}
\begin{figure}[t!]
             \begin{center}
              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/Fig8_pt_NSC32_Models.eps}}
              \end{center}
             \caption{NSC(3,2) as a function of the minimum $p_{\rm T}$ cut in $\PbPb$ collisions at $\snn=2.76$~TeV. Results are compared to various AMPT configurations and event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.}
             \label{fig:Figure_8}
\end{figure}

\begin{figure}[t!]
             \begin{center}
              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/Fig9_pt_NSC42_Models.eps}}
              \end{center}
             \caption{NSC(4,2) as a function of the minimum $p_{\rm T}$ cut in $\PbPb$ collisions at $\snn=2.76$~TeV. Results are compared to various AMPT configurations and event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.}
             \label{fig:Figure_9}
\end{figure}

>>>>

\begin{figure*}[t!]
            \begin{center}
                       \resizebox{0.51\textwidth}{!}{\includegraphics{figs/Fig1a_higherSC}}\hspace{-0.67cm}
                       \resizebox{0.51\textwidth}{!}{\includegraphics{figs/Fig1b_higherNSC}}
        \caption{The centrality dependence of SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonics for m = 3--5 and n = 2,3 in $\PbPb$ collisions at $\snn=2.76$~TeV. The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from \cite{ALICE:2016kpq} and shown as bands. The systematic and statistical errors are combined in quadrature for these lower order harmonic correlations. The SC(4,2) and SC(3,2) are downscaled by a factor of 0.1. Systematic uncertainties are represented with boxes for higher order harmonic correlations.}
        \label{fig:Figure_1}
              \end{center}
\end{figure*}

@@

\begin{figure}[t!]
	\begin{center}
        	\resizebox{0.92\columnwidth}{!}{\includegraphics{figs/Fig2_pt_SC_NSC}}
        \caption{SC(3,2) and SC(4,2) ((a) and (c)) as a function of minimum $p_{\rm T}$ cuts in $\PbPb$ collisions at $\snn=2.76$~TeV are shown in the left panels. The NSC(3,2) and NSC(4,2) ((b) and (d)) are shown in the right panels. Systematic uncertainties are represented with boxes.}         \label{fig:Figure_2}
        \end{center}   
\end{figure}

@@

\begin{figure}[t!]
	\begin{center}
        	\resizebox{0.92\columnwidth}{!}{\includegraphics{figs/Fig3_vn_xpt}}
        \caption{The individual flow harmonics $v_n$ for $n$ = 2--5 in $\PbPb$ collisions at $\snn=2.76$~TeV are shown in the left panels ((A), (B) and (C)). $v_4$ and $v_5$ are shown in the same panel (C). The $p_{\rm T, min}$ dependence of $v_n$ for $n$ = 2--4 is shown in the right panels ((a), (b) and (c)).}
        \label{fig:Figure_3}
        \end{center}   
\end{figure}

@@

\begin{figure}[t!]
            \begin{center}
                       \resizebox{\multfigsize\textwidth}{!}{\includegraphics{figs/Fig4_ModelComparison_EKRT}}
              \end{center}
        \caption{The centrality dependence of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV. Results are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}. The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations. Left (right) panels show SC($m$,$n$) (NSC($m$,$n$)).}        
        \label{fig:Figure_4}
\end{figure}

@@

\begin{figure}[t!]
	\begin{center}
        	\resizebox{\multfigsize\columnwidth}{!}{\includegraphics{figs/Fig5_ModelComparison_VISH}}
        \caption{The centrality dependence of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV. Results are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}. Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers. The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber and 0.16 for AMPT) are drawn as dashed lines. Left (right) panels show SC($m$,$n$)  (NSC($m$,$n$)).}
        \label{fig:Figure_5}
        \end{center}   
 \end{figure}

@@

 \begin{figure}[t!]
	\begin{center}
        	\resizebox{\multfigsize\columnwidth}{!}{\includegraphics{figs/Fig6_ModelComparison_AMPT}}
        \caption{The centrality dependence of SC($m$,$n$) and NSC($m$,$n$) in $\PbPb$ collisions at $\snn=2.76$~TeV. Results are compared to various AMPT models. Left (right) panels show SC($m$,$n$)  (NSC($m$,$n$).}
        \label{fig:Figure_6}
        \end{center}   
 \end{figure}

@@

\begin{figure}[t!]
            \begin{center}
                       \resizebox{0.99\textwidth}{!}{\includegraphics{figs/Fig7_chisqndf_bestfits_3pad}}
        \caption{The $\chisqndf$ values calculated by Eq.~\ref{Eq:chisq} are shown for SC($m$,$n$) (a), NSC($m$,$n$) (b) and individual harmonics $v_n$ (c). Results are for model calculations which are best in describing the SC observables for each of the three different types of models.}
        \label{fig:Figure_7}
              \end{center}
\end{figure}
The results for SC($m$,$n$) and NSC($m$,$n$) are presented in Fig.~\ref{fig:Figure_7}a and \ref{fig:Figure_7}b, respectively. The $\chisqndf$ values for the individual flow harmonics $v_n$ for $n$=2--4 are shown in Fig.~\ref{fig:Figure_7}c. We found that in case of the calculations from VISH2+1 with AMPT initial conditions ($\eta/s$ = 0.08) and the default configuration of the AMPT model, the $\chisqndf$ values for SC($m$,$n$) are larger than those for NSC($m$,$n$). This reflects the fact that the individual flow harmonics $v_n$ are not well described by those models compared to event-by-event EKRT+viscous hydrodynamics. This is quantified in Fig.~\ref{fig:Figure_7}c, where the $\chisqndf$ values for $v_n$ are much larger both for VISH2+1 and default AMPT calculations than event-by-event EKRT+viscous hydrodynamics.
The default configuration of the AMPT model gives the best $\chisqndf$ values for NSC($m$,$n$), especially for NSC(3,2). However the $\chisqndf$ values of this model are largest for $v_n$ among the models especially for $v_2$.

@@

\subsection{Transverse Momentum Dependence of Correlations between $v_2$ and $v_3$ and between $v_2$ and $v_4$}
\label{sec:ptdepsc}
\begin{figure}[t!]
             \begin{center}
              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/Fig8_pt_NSC32_Models}}
              \end{center}
             \caption{NSC(3,2) as a function of the minimum $p_{\rm T}$ cut in $\PbPb$ collisions at $\snn=2.76$~TeV. Results are compared to various AMPT configurations and event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.}
             \label{fig:Figure_8}
\end{figure}

\begin{figure}[t!]
             \begin{center}
              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/Fig9_pt_NSC42_Models}}
              \end{center}
             \caption{NSC(4,2) as a function of the minimum $p_{\rm T}$ cut in $\PbPb$ collisions at $\snn=2.76$~TeV. Results are compared to various AMPT configurations and event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}.}
             \label{fig:Figure_9}
\end{figure}
